% -*- bidi-paragraph-direction: left-to-right -*-

\documentclass[11pt]{article}

\usepackage[margin=1in,top=1.25in,bottom=1.25in]{geometry}
\usepackage{soul}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{setspace}
\usepackage{arabxetex}

\setuldepth{sh}

\setmainfont[Ligatures=TeX]{GaramondPremrPro}[
  Path           = /Users/johnw/Library/Fonts/ ,
  Extension      = .otf ,
  BoldFont       = *-Smbd ,
  ItalicFont     = *-It ,
  BoldItalicFont = *-SmbdIt
]

\newfontfamily\arabicfont{Scheherazade}[
  Path        = /Users/johnw/Library/Fonts/ ,
  Extension   = .ttf ,
  UprightFont = *RegOT ,
  Script      = Arabic
]

\newfontfamily\headwordfont[Ligatures=TeX]{Georgia}[
  Path           = /Users/johnw/Library/Fonts/ ,
  Extension      = .ttf ,
  UprightFont    = * ,
  BoldFont       = * Bold ,
  ItalicFont     = * Italic ,
  BoldItalicFont = * Bold Italic ,
  Script         = Arabic
]

\newenvironment{orig}
  {\begin{farsi}[voc]}
  {\end{farsi}}

\newenvironment{trans}
  {\Large\begin{spacing}{1.2}\raggedright}
  {\end{spacing}}

\newenvironment{word}
  {\begin{longtable}[t]{p{3.5in}@{\hspace{3em}}p{2in}}}
  {\end{longtable}}

\newcommand{\ayat}[2]{\begin{orig}#1\end{orig} & \begin{trans}#2\end{trans}}
\newcommand{\heading}[2]{\textsc{\textbf{#1}} % \ (\##2)
}
\newcommand{\define}[3]{\textfarsi[voc]{\Huge
    \textbf{#1}}\hspace{3mm}{\headwordfont \large
    \textit{#2}}\hspace{3mm}{\Large #3} \\[3ex]}
\newcommand{\fulldefine}[3]{\textfarsi[voc]{\Huge
    \textbf{#1}}\hspace{3mm}{\headwordfont \large
    \textit{#2}}\vspace{-1ex}\begin{quote}\Large #3\end{quote}\vspace{1ex}}

\title{
\Huge
\vspace*{2in}
Selections from \\
the Sacred Writings \\
\vspace{.25in}
\fontsize{48}{36}
\begin{arab}
\end{arab}
\vspace{1in}}
\author{\LARGE Bahá’u’lláh and `Abdu'l-Bahá}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\newpage

\fontsize{24}{32}

\begin{word}
\ayat{
اِلهَا پَروَردِگارا مَحبوبا مَقصُودا
}{O God, O God, my Beloved, the Goal of my Desire!} \\ \ayat{
به تو آمده ام و از تو می طلبم

آنچه را كه سببِ بخششِ تو است
}{I stand before Thee and beseech Thee by reason of Thy forgiveness,} \\ \ayat{
توئی بحرِ جود و مالكِ وجود
}{O Thou Who art the Ocean of bounty and the King of existence,} \\ \ayat{
لازال

لحاظتِ علّتِ ظهورِ بخشش و عطا
}{O Thou Who hast caused both forgiveness and tenderness to appear.} \\ \ayat{
عبادِ خود را محروم منما
}{Deny not Thy servants} \\ \ayat{
و از بِساطِ قُدس و قُرب منع مفرما
}{and withhold them not from Thy holiness and nearness.} \\ \ayat{
توئی بخشنده و مهربان
}{Thou art the Forgiving and the Kind.} \\ \ayat{
لا اِلهَ اِلّا اَنتَ العَزيزُ المَنّان
}{No God is there but Thee, the Almighty, the Most Bountiful.}
\end{word}

\newpage

\begin{word}
\ayat{
ای احبّای حقّ
}{O ye the beloved of the one true God!} \vspace{-1ex}\\ \ayat{
از مَفازَۀِ ضَیِّقِۀِ نفس و هویٰ
}{Pass beyond the narrow retreats of your evil and corrupt desires,} \vspace{-1ex}\\ \ayat{
به فَضاهایِ مُقَدَّسِۀِ اَحَدِیِّه بِشتابید
}{and advance into the vast immensity of the realm of God,} \vspace{-1ex}\\ \ayat{
و در حَدِیقِۀِ تَقدیس و تَنزیه

مَأویٰ گیرید
}{and abide ye in the meads of sanctity and of detachment,} \\ \ayat{
تا از نَفَحاتِ اَعمالِیِّه کُلّ بَرِیِّه

بشاطیِ عِزِّ اَحَدِیِّه تَوَجُّه نمایند
}{that the fragrance of your deeds may lead the whole of mankind to the ocean
  of God’s unfading glory.} \vspace{-1ex}\\ \ayat{
اَبَداً در اُمورِ دُنیا و مَا یَتَعَلَّقُ بها

و رُؤسایِ ظاهِرۀِ آن تَکَلُّم جایز نه
}{Forbear ye from concerning yourselves with the affairs of this world and all
  that pertaineth unto it, or from meddling with the activities of those who
  are its outward leaders.}
\end{word}

% \newpage

% \begin{minipage}[t]{0.48\textwidth}
% \define{صاحبان}{sá\d{h}ibán}{owners}
% \fulldefine{هدهد}{hudhud}{The hoopoe bird, often a guide in Sufi literature.}
% \end{minipage}

\newpage

\begin{word}
\ayat{
اللّه ابهی
}{} \vspace{-1ex}\\ \ayat{
ای متوجّه اِلی اللّه
}{O thou who art turning thy face towards God!} \vspace{-1ex}\\ \ayat{
چشم از جميعِ ماسِوی بَر بَند
}{Close thine eyes to all things else,} \vspace{-1ex}\\ \ayat{
و به مَلَکوتِ ابهی بَر گشا
}{and open them to the realm of the All-Glorious.} \vspace{-1ex}\\ \ayat{
آنچه خواهی از او خواه
}{Ask whatsoever thou wishest of Him alone;} \vspace{-1ex}\\ \ayat{
و آنچه طلبی از او طلب
}{seek whatsoever thou seekest from Him alone.} \vspace{-1ex}\\ \ayat{
به نظری

صد هزار حاجاتت روا نمايد
}{With a look He granteth a hundred thousand hopes,} \vspace{-1ex}\\ \ayat{
و به التفاتی

صد هزار درد بی درمان دوا کند
}{with a glance He healeth a hundred thousand incurable ills,} \vspace{-1ex}\\ \ayat{
و به انعطافی

زخم‌ها را مَرهم نهد
}{with a nod He layeth balm on every wound,} \vspace{-1ex}\\ \ayat{
و به نگاهی

دل‌ها را از قيدِ غم برهاند
}{with a glimpse He freeth the hearts from the shackles of grief.}
\end{word}

\newpage

\begin{word}
\ayat{
آنچه کند او کند
}{He doeth as He doeth,} \vspace{-1ex}\\ \ayat{
ما چه توانيم کرد
}{and what recourse have we?} \vspace{-1ex}\\ \ayat{
يَفعل ما يَشاء
}{He carrieth out His Will,} \vspace{-1ex}\\ \ayat{
و يَحکُمُ ما يُريد است
}{He ordaineth what He pleaseth.} \vspace{-1ex}\\ \ayat{
پس سَرِ تسليم نـِه
}{Then better for thee to bow down thy head in submission,} \vspace{-1ex}\\ \ayat{
و توکّل بر رَبِّ رحيم بـِه
}{and put thy trust in the All-Merciful Lord.} \vspace{-1ex}\\ \ayat{
والبهاء عليک

ع ع
}{}
\end{word}

\newpage

\begin{word}
\ayat{
حکایت آورده‌اند
}{The story is told} \vspace{-1ex}\\ \ayat{
که عارف الهی با عالم نحوی

همراه شدند و همراز گشتند
}{of a mystic knower who went on a journey with a learned grammarian for a
  companion.} \vspace{-1ex}\\ \ayat{
تا رسیدند بشاطی بحر العظمة
}{They came to the shore of the Sea of Grandeur.} \vspace{-1ex}\\ \ayat{
عارف بی ‌تأمّل توسّل فرموده

بر آب راند
}{The knower, putting his trust in God, straightway ﬂung himself into the
  waves,} \vspace{-1ex}\\ \ayat{
و عالم نحو

چون نقشِ بر آب محو گشته

مبهوت ماند
}{but the grammarian stood bewildered and lost in thoughts that were as words
  traced upon the water.} \\ \ayat{
بانگ زد عارف

که چون عنان پیچیدی
}{The mystic called out to him, “Why dost thou not follow?”}
\end{word}

\newpage

\begin{word}
\ayat{
گفت
}{The grammarian answered,} \vspace{-1ex}\\ \ayat{
ای برادر چه کنم
}{“O brother, what can I do?} \vspace{-1ex}\\ \ayat{
چون پای رفتنم نیست

سَرْ نَهادن اولیٰ بود
}{As I dare not advance, I must needs go back again.”} \\ \ayat{
گفت
}{Then the mystic cried,} \vspace{-1ex}\\ \ayat{
آنچه از سیبویه و قولویه

اَخْذ نموده‌ئی

و یا از مطالب ابن حاجب

و ابن مالک

حَمْل فرموده ئی

بریز و از آب بگذر
}{“Cast aside what thou hast learned from Síbavayh and Qawlavayh, from
  Ibn-i-Hájib and Ibn-i-Málik, and cross the water!”\vspace{15ex}} \\ \ayat{
محو میباید نه نحو این را بدان
}{With renunciation, not with grammar’s rules, one must be armed:} \vspace{-1ex}\\ \ayat{
گر تو محوی بی خطر در آب ران
}{Be nothing, then, and cross this sea unharmed.}
\end{word}

\newpage

\begin{word}
\ayat{
هو الله

ای طالب ملکوت

به الطاف حضرت پروردگار

اميدوار باش

و از مَصائِبِ شَديدۀِ اين جهان

نااميد مگرد

الحمدلله

خدای مهربان داری

که طَبيبِ هر بيمار است

و غَمخوارِ هر مُبتَلا

پَناهِ يَتيمان است

و مُعين بيکَسان

و بينهايت مِهرِبان
}{}
\end{word}

\newpage

\begin{word}
\ayat{
اگر بدانی که قلب عبد البهاء

چه قَدر مهربان است

البتّه از شِدَّتِ فَرَح و سُرور

پَرواز نمائی

و فَريادِ واطوبىٰ

به اُوجِ آسمان رِسانی


والبهاو عَلَیکْ

عبد البهاء عبّاس
}{}
\end{word}

\newpage

% }{} \\ \ayat{
\begin{word}
\ayat{
زبانِ خِرَد میگوید
}{The Tongue of Wisdom proclaimeth:} \vspace{-1ex}\\ \ayat{
هر که دارایِ من نباشد

دارایِ هیچ نه
}{He that hath Me not is bereft of all things.} \vspace{-1ex}\\ \ayat{
از هر چه هست بگذرید

و مرا بیابید
}{Turn ye away from all that is on earth and seek none else but Me.} \\ \ayat{
منم آفتابِ بینش

و دریایِ دانش
}{I am the Sun of Wisdom and the Ocean of Knowledge.} \vspace{-1ex}\\ \ayat{
پژمردگان را تازه نمایم

و مردگان را زنده کنم
}{I cheer the faint and revive the dead.} \\ \ayat{
منم آن روشنائی

که راهِ دیده بنمایم
}{I am the guiding Light that illumineth the way.} \vspace{-1ex}\\ \ayat{
و منم شاهبازِ دستِ بینیاز
}{I am the royal Falcon on the arm of the Almighty.} \vspace{-1ex}\\ \ayat{
پرِ بستگان را بگشایم

و پرواز بیاموزم
}{I unfold the drooping wings of every broken bird and start it on its
  flight.}
\end{word}

\newpage

% }{} \\ \ayat{
\begin{word}
\ayat{
و بِه قَدَمِ یَقین
}{Thus with steadfast steps} \vspace{-1ex}\\ \ayat{
در صِراطِ حَقُّ الیقین

قَدَم گذاریم
}{we may tread the Path of certitude,} \\ \ayat{
که لِعَلّْ نسیمِ رضا
}{that perchance the breeze that bloweth
from the meads of the good-pleasure of God} \vspace{-1ex}\\ \ayat{
از ریاضِ قبولِ الهی بِوَزَد
}{may waft upon us the sweet savours
    of divine acceptance,} \vspace{-1ex}\\ \ayat{
و این فانیان را
}{and cause us, vanishing mortals that we are,} \vspace{-1ex}\\ \ayat{
بملکوتِ جاودانی رِساند
}{to attain unto the Kingdom of everlasting glory.}
\end{word}

\newpage

\begin{word}
\ayat{
هو الله
}{} \\ \ayat{
رشحِ عما از جذبۀ ما میریزد

سرّ وفا از نغمۀ ما میریزد
}{From Our rapture, the Clouds of the Pre-Eternal rain down...

From Our melody the secrets of devotion rain down...
} \\ \ayat{
از باد صَبا مُشگ خطا گشته پدید

وین نفخۀ خوش از جَعدِۀ ما میریزد
}{
A wind stirs from Sheba carrying the musk of Cathay,

While from Our locks fragrant breezes rain down...
} \\ \ayat{
شمسِ طَراز از طَلعَت حَقّ کرده طُلوع

سِرّ حقیقت بین کَز وجهۀ ما میریزد
}{
The Sun of adornment rises from the countenance of Truth

Behold! From Our visage the mysteries of truth rain down...
} \\ \ayat{
بحرِ صَفا از موجِ لِقا کرده خُروش

وین طُرفهْ عطا از جذبۀ ما میریزد
}{
The sea of purity surges through a wave of reunion

From Our ecstasy these precious gifts rain down...
} \\ \ayat{
گنجینۀ حُبّ در سینۀ فا گشته نَهان

زین گَنجِ مُحَبَّت دُرِّ وفا ميريزد
}{
Treasuries of love lay concealed in the breast of Fá

From this trove of affection pearls of faith rain down...
} \\ \ayat{
بِهجَتِ مُل از نَظرِۀ گُل شد ظاهر

این رَمزِ ملیح از رَنِّۀ را میریزد
}{
The choicest wine appears through a glance at this rose


From the songs of Rá heart-stirring secrets rain down...
} \\ \ayat{
نُقرۀ ناقوری جذبۀ لاهوتی

این هر دو بیک نَفخِه از جَوِّ سَما میریزد
}{
The silver-white trumpet and the rapture of the Divine

Both of these, through one blow of heaven's breath, rain down...
} \\ \ayat{
دَورِ اَنَا هُو از چهرۀ ما کرده بُروز

کَورِ هُوَ هُو از نَفخِۀ ما میریزد
}{
From Our appearence the Day of ``I am He'' beams forth;

From Our breath the Age of ``He is He'' rains down...
} \\ \ayat{
کوثرِ حقّ از کاسۀ دل گشته هُویدا

وین ساغرِ شَهْد از لَعلِ بها میریزد
}{
The Kuwthar of heaven flows from the cup of Our heart

From the lips of Bahá sweet draughts of honey rain down...
} \\ \ayat{
یومِ خدا از جِلوِۀ ربّ شد کامل

این نَغزِ حَدیث از غَنۀ طا میریزد
}{
The Day of God is fulfilled by Our Lord's unveiling

From the riches of Tá what graceful tales rain down...
} \\ \ayat{
طَفحِ بهائی بین رشح عمائی بین

کِاین جُمله زِ یک نغمه از لَحنِ خدا میریزد
}{
What overflowing glory! What showers from these clouds!

From but one of God's songs do these words rain down...
} \\ \ayat{
ماهیِ سرمد بین طَلعِ مُنَزَّه بین

صَدرِ مُمَرَّد بین کز عَرشِ علا میریزد
}{
Behold the great Leviathan! Behold His blameless countenance!

Behold His lofty seat! that from the exalted throne rains down...
} \\ \ayat{
نَخلِۀ طوبیٰ بین رَنِّۀ ورقا بین

غَنِّۀ ابهی بین کَز لَمْعِ صَفا میریزد
}{
Behold of the palm of paradise! Behold the melody of the dove!

Heark the paeans of Abhá, that in pure splendor rain down...
} \\ \ayat{
آهنگِ عراقی بین دَفِّ حجازی بین

کَفِّ الهیٰ بین کز جذبه لا میریزد
}{
Hear the Persian melody, and the Arab drum!

The song of God that from the joy of Lá rains down...
} \\ \ayat{
طَلعَةِ لاهوتی بین حوریِ هاهوتی بین

جِلوِۀ ناسوتی بین کز سِرِّ عما میریزد
}{
Behold the Divine Appearance, the Maid of His Threshold!

By the secret of Pre-existence her mortal guise rains down...
} \\ \ayat{
وَجۀ باقی بین چِهرۀ ساقی بین

رَقِّ زُجاجی بین کز کوبۀ ما میریزد
}{
Behold the Immortal Face, and the cup-bearer's glance!

Behold our gleaming chalice whose crystal waters rain down...
} \\ \ayat{
آتَشِ موسیٰ بین بَیضِۀ بَیضا بین

سینۀ سینا بین کز کفِّ سَنا میریزد
}{
Behold the flame of Moses! Behold its gleaming light!

From our hand of splendor, how the heart of Sinai rains down...
} \\ \ayat{
نالِۀ مَستان بین حالتِ بُستان بین

جذبۀ هَستان بین کز صحنِ لِقا میریزد
}{
Hear the lament of the drunkards; observe the state of the gardens;

Witness how from our court the ecstasy of existence rains down...
} \\ \ayat{
غُنچۀ هائی بین طُرّۀ بائی بین

رَنِّۀ نائی بین کز کِلکِ بها میریزد
}{
Behold the budding blooms of Há; the curling locks of Bá

From the tresses of Bahá, hear the song of Ná rain down...
} \\ \ayat{
طَفحِ طَهور است این رَشح طَهور است این

غَن طُیور است این کز عِین فَنا میریزد
}{
This is the overflowing ablution; this is the cleansing water!

This is the trill of birds, that from annihilating eyes rain down...
}
\end{word}

\end{document}
