% -*- bidi-paragraph-direction: left-to-right -*-

\documentclass[14pt]{extarticle}

\include{quotes}
\setlength{\quotesep}{0ex}
\setlength{\quoteparindent}{0em}
\def\notestyle{nonote}

\begin{document}

\begin{hafez}{}{}
  Thus I exhort each of you\dots{} \\
  to sacrifice all your \textbf{thoughts}, \textbf{words} and \textbf{actions} \\
  to bring the knowledge of the Love of God into every heart.
\end{hafez}

\noindent\rule{2cm}{0.4pt}

\begin{hafez}{SLH}{}
  Say: Were He to utter but one word, that word alone would exceed in
  sweetness all the sayings of men.
\end{hafez}

\noindent\rule{2cm}{0.4pt}

\begin{hafez}{GWB}{pp.~8--9}
  Every eye, in this Day, should seek what will best promote the Cause of God. \\
  He, Who is the Eternal Truth, beareth Me witness! \\
  Nothing whatsoever can, in this Day, inflict a greater harm upon this Cause \\
    \mbox{\hspace{0.1in}}than \textbf{dissension} and \textbf{strife},
      \textbf{contention}, \textbf{estrangement} and \textbf{apathy}, \\
    \mbox{\hspace{0.1in}}among the loved ones of God. \\
  Flee them, through the power of God and His sovereign aid, \\
    \mbox{\hspace{0.1in}}and strive ye to knit together the hearts of men, \\
    \mbox{\hspace{0.1in}}in His Name, the Unifier, the All-Knowing, the All-Wise.
\end{hafez}

\noindent\rule{2cm}{0.4pt}

\begin{hafez}{GWB}{\#144, p.~355}
  Wert thou to consider this world, \\
    \mbox{\hspace{0.1in}}and realize how fleeting are the things that pertain unto it, \\
  thou wouldst choose to tread no path \\
    \mbox{\hspace{0.1in}}except the path of service to the Cause of thy Lord. \\
  None would have the power to deter thee from celebrating His praise, \\
  though all men should arise to oppose thee.
\end{hafez}

\newpage

\begin{hafez}{TDP}{pp.~52--53}
  The divine friends must be attracted to and enamored of each other \\
    \mbox{\hspace{0.1in}}and ever be ready and willing to sacrifice their own lives for each other. \\
  Should one soul from amongst the believers meet another, \\
    \mbox{\hspace{0.1in}}it must be as though a thirsty one with parched lips \\
      \mbox{\hspace{0.2in}}has reached to the fountain of the water of life, \\
    \mbox{\hspace{0.1in}}or a lover has met his true beloved.

  For one of the greatest divine wisdoms regarding the appearance of the holy Manifestations is this: \\
    \mbox{\hspace{0.1in}}The souls may come to know each other \\
      \mbox{\hspace{0.2in}}and become intimate with each other; \\
    \mbox{\hspace{0.1in}}the power of the love of God \\
      \mbox{\hspace{0.2in}}may make all of them the waves of one sea, \\
      \mbox{\hspace{0.2in}}the flowers of one rose garden, \\
      \mbox{\hspace{0.2in}}and the stars of one heaven. \\
  This is the wisdom for the appearance of the holy Manifestations!

  When the most great bestowal reveals itself in the hearts of the believers, \\
    \mbox{\hspace{0.1in}}the world of nature will be transformed, \\
    \mbox{\hspace{0.1in}}the darkness of the contingent being will vanish, \\
    \mbox{\hspace{0.1in}}and heavenly illumination will be obtained. \\
  Then the whole world will become the Paradise of Abhá, \\
    \mbox{\hspace{0.1in}}every one of the believers of God will become a blessed tree, \\
    \mbox{\hspace{0.1in}}producing wonderful fruits.
\end{hafez}

\newpage

\begin{hafez}{}{}
  Within the treasury of Our Wisdom \\
    \mbox{\hspace{0.1in}}there lieth unrevealed a knowledge, \\
  one word of which, \\
    \mbox{\hspace{0.1in}}if we chose to divulge it to mankind, \\
  would cause every human being \\
    \mbox{\hspace{0.1in}}to recognize the Manifestation of God \\
    \mbox{\hspace{0.1in}}and to acknowledge His omniscience, \\
  would enable every one to discover the secrets of all the sciences, \\
    \mbox{\hspace{0.1in}}and to attain so high a station \\
    \mbox{\hspace{0.1in}}as to find himself wholly independent of all past and future learning.
\end{hafez}

\noindent\rule{2cm}{0.4pt}

\begin{hafez}{}{}
  He is the \textbf{King}\dots{} \\
  Verily this is that Most Great Beauty\dots{} \\
  O Ahmad! Bear thou witness\dots{} \\
  Say: O people be obedient\dots{}

  Thus doth the \textbf{Nightingale}\dots{} \\
  O people, if ye deny these verses\dots{} \\
  Nay, by the One in Whose hand is my soul\dots{}

  O Ahmad! \textbf{Forget not} My bounties\dots{} \\
  Be thou as a flame of fire\dots{} \\
  And if thou art overtaken\dots{} \\
  Rely upon God\dots{}
  Thus have their \textbf{superstitions}\dots{} \\
  Be thou assured in thyself\dots{}

  \textbf{Learn well} this Tablet, O Ahmad\dots{} \\
  By God! Should one\dots{} \\
  Verily, He is the Merciful\dots{}
\end{hafez}{}

\newpage

\begin{hafez}{}{}
  In the name of God, the Most Ancient, the Most Great.

  \begin{tabular}{|l|l|l|}
  \hline
  \textbf{hearts}      & gleaming    & O Beloved     \\
  \textbf{near}        & shining     & O Desire      \\
  \textbf{bodies}      & ocean       & O Enchanter   \\
  \textbf{hands}       & rains       & O Answerer    \\
  \textbf{infidels}    & power       & O Conqueror   \\
  \textbf{barking}     & lion        & O Chastiser   \\ \hline

  \multicolumn{3}{c}{}           \\ \hline
  \textbf{Coldness}    & warmth      & O Fire        \\
  \textbf{Calamity}    & signs       & O Salvation   \\
  \textbf{Darkness}    & brightness  & O Radiance    \\
  \textbf{necks}       & swords      & O Destroyer   \\
  \textbf{Abasement}   & emblems     & O Glory       \\
  \textbf{Sorrows}     & joy         & O Delight     \\ \hline

  \multicolumn{3}{c}{}           \\ \hline
  \textbf{Anguish}     & ensigns     & O Joy         \\
  \textbf{Dawning}     & fingers     & O Power       \\
  \textbf{thirst}      & river       & O Mercy       \\
  \textbf{Greed}       & embodiments & O Lord        \\
  \textbf{Wronged}     & hosts       & O Sovereign   \\
  \textbf{forsaken}    & emblems     & O Trust       \\ \hline

  \multicolumn{3}{c}{}           \\ \hline
  \textbf{agonies}     & surging     & O Life        \\
  \textbf{whisperings} & meteor      & O Light       \\
  \textbf{drunkenness} & daysprings  & O Desire      \\
  \textbf{Wronged}     & radiance    & O Light       \\
  \textbf{forbidden}   & melodies    & O Nightingale \\
  \textbf{people}      & exponents   & O Assurance   \\ \hline

  \multicolumn{3}{c}{}           \\ \hline
  \textbf{Bahá}        & Ark         & O Savior      \\
  \textbf{Dayspring}   & sun         & O Lightgiver  \\
  \textbf{lamps}       & signs       & O Mover       \\
  \textbf{Canst}       & pen         & O Beloved     \\
  \textbf{branches}    & banners     & O Champion    \\
  \textbf{Face}        & breezes     & O Mercy       \\ \hline

  \multicolumn{3}{c}{}           \\ \hline
  \textbf{robe}        & vesture     & O Adorner     \\
  \textbf{sea}         & waves       & O Desire      \\
  \textbf{door}        & key         & O Unlocker    \\
  \textbf{leaves}      & downpour    & O Giver       \\
  \textbf{universe}    & breezes     & O Forgiver    \\
  \textbf{Youth}       & rain        & O Bestower    \\ \hline
  \end{tabular}

  O Supreme Pen, \\
  We have \textbf{heard} Thy most sweet call in the eternal realm: \\
  Give Thou \textbf{ear} unto what the Tongue of Grandeur uttereth, \\
  O \textbf{Wronged} One of the worlds!

  \begin{tabular}{|l|l|l|}
  \hline
  \textbf{cold}     & heat     & O Expounder \\
  \textbf{calamity} & sun      & O Light     \\
  \textbf{Lament}   & created  & O Patience  \\
  \textbf{sweet}    & yearning & O Love      \\
  \textbf{banner}   & bounty   & O Rapture   \\ \hline

  \multicolumn{3}{c}{} \\ \hline
  \textbf{aloneness} & patient    & O Thou Exile     \\
  \textbf{abasement} & affliction & O Pride          \\
  \textbf{hearts}    & overlook   & O Thou Concealer \\
  \textbf{swords}    & shafts     & O Thou Sacrifice \\
  \textbf{wail}      & weep       & O Thou Who       \\ \hline
  \end{tabular}

  \mbox{}

  Verily, I have heard Thy \textbf{call}, O All-Glorious Beloved; \\
  and now is the \textbf{face} of Bahá flaming with the heat of tribulation \\
  and with the \textbf{fire} of Thy shining word, \\
  and He hath \textbf{risen} up in faithfulness at the place of sacrifice, \\
  looking toward Thy \textbf{pleasure}, O Ordainer of the worlds.

  O `Alí-Akbar, \\
  \textbf{thank} thy Lord for this Tablet \\
  whence thou canst \textbf{breathe} the fragrances of My meekness, \\
  and know what hath \textbf{beset} Us in the path of God, \\
  the \textbf{Adored} of all the worlds.

  Should all the \textbf{servants} read and ponder this, \\
  there shall be \textbf{kindled} in their veins \\
  a \textbf{fire} that shall set aflame the worlds.
\end{hafez}

\newpage

\begin{hafez}{}{}
  \begin{quote}
    \emph{.1 gaze to the right and to the left}
  \end{quote}

  O Thou Who art the Lord of all names and the Maker of the heavens! \\
  I beseech Thee by them Who are the Daysprings\dots{}

  \begin{quote}
    \emph{.2 raise his hands}
  \end{quote}

  O Thou the Desire of the world and the Beloved of the nations! \\
  Thou seest me turning toward Thee\dots{} \\
  I am Thy servant, O my Lord, and the son of Thy servant. \\
  Behold me standing ready to do Thy will and Thy desire\dots{} \\
  I implore Thee by the Ocean of Thy mercy and\dots{} \\
  By Thy might which is far above all mention and praise! \\
  Whatsoever is revealed by Thee is the desire\dots{} \\
  O God, my God! Look not upon my hopes and my doings, nay rather\dots{} \\
  By Thy Most Great Name, O Thou Lord of all nations! \\
  I have desired only what Thou didst desire, and love only what Thou dost love.

  \begin{quote}
    \emph{.3 kneel}
  \end{quote}

  Exalted art Thou\dots{}

  \begin{quote}
    \emph{.4 stand}
  \end{quote}

  Make my prayer, O my Lord, a fountain of living waters\dots{}

  \begin{quote}
    \emph{.5 raise his hands}
  \end{quote}

  O Thou in separation from Whom hearts and souls have melted\dots{} \\
  I implore Thee by Thy Name through which Thou hast subdued\dots{} \\
  Thou seest, O my Lord, this stranger hastening to his most exalted home\dots{} \\
  Thine is the authority to command whatsoever Thou willest. \\
  I bear witness that Thou art to be praised in Thy doings\dots{}

  \begin{quote}
    \emph{.6 raise his hands, and repeat three times}
  \end{quote}

  Thou seest, O my God, how my spirit hath been stirred up\dots{} \\
  I love, in this state, O my Lord, to beg of Thee\dots{}

  \begin{quote}
    \emph{.7 raise his hands twice}
  \end{quote}

  There is no God but Thee, the Almighty, the All-Bountiful. \\
  There is no God but Thee, the Ordainer, both in the beginning and in the end. \\
  O God, my God! Thy forgiveness hath emboldened me\dots{} \\
  Who, otherwise, am I that I should dare to stand\dots{} \\
  Thou seest, O my Lord, this wretched creature knocking\dots{} \\
  Thine is the command at all times, O Thou Who art\dots{}

  \newpage

  \begin{quote}
    \emph{.8 raise his hands thrice}
  \end{quote}

  \textbf{Greater is God than every great one!}

  \begin{quote}
    \emph{.9 kneel}
  \end{quote}

  Too high art Thou\dots{} \\
  I testify that Thou hast been sanctified\dots{} \\
  No God is there but Thee, the Most Exalted, the All-Glorious.

  \begin{quote}
    \emph{.10 seat himself}
  \end{quote}

  I testify unto that whereunto have testified\dots{} \\
  I testify that it is He Whose name\dots{}

  \begin{quote}
    \emph{.11 stand erect}
  \end{quote}

  O Lord of all being and Possessor of all things visible and invisible! \\
  Thou dost perceive my tears\dots{} \\
  By Thy might! My trespasses have kept me back\dots{} \\
  Thy love, O my Lord, hath enriched me\dots{} \\
  I entreat Thee by Thy footsteps in this wilderness\dots{}

  \begin{quote}
    \emph{.12 repeat the Greatest Name thrice, and bend down}
  \end{quote}

  Praise be to Thee, O my God, that Thou hast aided me\dots{}

  \begin{quote}
    \emph{.13 rise}
  \end{quote}

  O God, my God! My back is bowed by the burden of my sins\dots{} \\
  Whenever I ponder my evil doings and Thy benevolence\dots{} \\
  By Thy Beauty, O Thou the Desire of the world! \\
  I blush to lift up my face to Thee, and my longing hands\dots{} \\
  Thou seest, O my God, how my tears prevent me\dots{} \\
  I implore Thee by the signs of Thy Kingdom\dots{}

  \begin{quote}
    \emph{.14 repeat the Greatest Name thrice, and kneel}
  \end{quote}

  Praise be unto Thee, O our God, that Thou hast sent down unto us\dots{} \\
  Protect us, we beseech Thee, O my Lord, from the hosts\dots{} \\
  Thou, in truth, art the Mighty, the All-Knowing.

  \begin{quote}
    \emph{.15 raise his head, and seat himself}
  \end{quote}

  I testify, O my God, to that whereunto\dots{} \\
  The kingdoms of earth and heaven are Thine, O Lord of the worlds!
\end{hafez}{}

\newpage

\begin{hafez}{}{}
  He is the All-Glorious!

  O God, my God! Lowly and tearful\dots{} \\
  Lord! He is a poor and lowly servant of Thine\dots{} \\
  O Lord, my God! Give me Thy grace\dots{} \\
  With this prayer doth Thy servant call Thee\dots{} \\
  Thou art the Bestower\dots{}
\end{hafez}

\noindent\rule{2cm}{0.4pt}

\begin{hafez}{SWB}{p.~216}
  O my God, O my Lord, O my Master! \\
  I beg Thee to forgive me \\
  for seeking any \textbf{pleasure} save Thy love, \\
  or any \textbf{comfort} except Thy nearness, \\
  or any \textbf{delight} besides Thy good-pleasure, \\
  or any \textbf{existence} other than communion with Thee.
\end{hafez}

\newpage

\begin{hafez}{}{}
  \begin{farsi}[voc]
\LARGE
یا إلهی \\
اسمك شفائی \\
و ذکرك دوائی \\
و قربك رجائی \\
و حبّك مؤنسی \\
و رحمتك طبيبی و معينی \\
فی الدّنیا و الآخرة \\
و انّك أنت المعطي العليم الحکيم
  \end{farsi}
\end{hafez}

\newpage

\thispagestyle{empty}


\begin{hafez}{}{}
  \begin{arab}[voc]
\Huge

\begin{tabular}{|rrr||rrr|}
\hline
عَلِي  &  وَفِي  &  بَهِي & عَظُوْم &  قَدُوْم &  كَرُوْم \\
سُلْطَان  &  رَفْعَان  &  دَيَّان & مَحْفُوْظ &  مَحْظُوْظ &  مَلْحُوْظ \\
أَحَد &  صَمَد &  فَرْد & عَطُوْف &  رَؤُوْف &  لَطُوْف \\
سُبْحَان &  قُدْسَان &  مُسْتَعان & مَلَاذ &  مَعَاذ &  مُسْتَعَاذ \\ \hline
عَلِيْم &  حَكِيْم &  عَظِيْم & غَيَّاث &  مُسْتَغَاث &  نَفَّاث \\
رَحْمَن &  عَظْمَان &  قَدْرَان & كَاشِف &  نَاشِف &  عَاطِف \\
مَعْشُوْق &  مَحْبُوْب &  مَجْذُوْب & جَان &  جَانَان &  إِيْمَان \\
عَزِيْز &  نَصِيْر &  قَدِيْر & سَاقِيْ  &  عَالِيْ  &  غَالِيْ \\ \hline
حَاكِم &  قَائِم &  عَالِم & ذِكْرَ الأَعْظَمِ  &  إِسْمَ الأَقْدَمِ  &  رَسْمَ الْأَكرَمِ \\
رُوْح &  نُوْر &  ظُهُوْر & سُبوْح &  قُدوْس &  نُزوْه \\
مَعْمُوْر &  مَشْهُوْر &  مَسْتُوْر & فَتَّاح &  نَصَّاح &  نَجَّاح \\
غَائِب &  غَالِب &  وَاهِب & حَبِيْب &  طَبِيْب &  جَذِيْب \\ \hline
قَادِر &  نَاصِر &  سَاتِر & جَلَال &  جَمَال &  فَضَّال \\
صَانِع &  قَانِع &  قَالِع & وَاثِق &  عَاشِق &  فَالِقي \\
طَالِع &  جَامِع &  رَافِعي & وَهَّاج &  بَلَّاج &  بَهَّاج \\
بَالِغ &  فَارِغ &  سَابِغ & وَهَّاب &  عَطَّاف &  رَآَّف \\\hline
نَافِع &  شَافِع &  دَافِع & تَائِب &  نَائِب &  ذَاوِب \\
جَلِيْل &  جَمِيْل &  فَضِيْل & ثَابِت &  نَابِت &  ذاوِت \\
عَادِل &  فَاضِل &  بَاذِل & حَافِظ &  لاَحِظ &  لاَفِظ \\
قَيوْم &  دَيْمُوْم &  عَلُوْم & & & \\ \hline
\end{tabular}

\newpage
\LARGE
بِسْمِ اللهِ الأَمْنَعِ الأَقْدَسِ الأَرْفَعِ الأَبْهَى \\

يَا ظَاهِرٌ مَسْتُوْرٌ يَا غَائِبٌ مَشْهُوْرٌ يَا نَاظِرٌ مَنْظُوْرٌ

أَنْتَ الكَافِي وَأَنْتَ الشَّافِي وَأَنْتَ البَاقِي يَا بَاقِي \\

يَا قَاتِلَ عُشَّاقٍ يَا وَاهِبَ فُسَّاقٍ

يَا كَافِي بِكَ يَا كَافِي

يَا شَافِي بِكَ يَا شَافِي

يَا بَاقِي بِكَ يَا بَاقِي

أَنْتَ البَاقِي يَا بَاقِي \\

سُبْحَانَكَ اللَّهُمَّ يَا إِلَهِي أَسْأَلُكَ بِجُوْدِكَ الَّذي بِهِ فَتَحْتَ أَبْوَابَ الفَضْلِ وَالعَطَاءِ وَبِهِ اسْتَقَرَّ هَيْكَلُ قُدْسِكَ عَلَى عَرْشِ البَقاءِ وَبِرَحْمَتِكَ الَّتِي بِهَا دَعَوْتَ المُمْكِنَاتِ عَلَى خُوَانِ مَكْرُمَتِكَ وَإِنْعَامِكَ وَبِعِنَايَتِكَ الَّتِي بِهَا أَجَبْتَ فِي نَفْسِكَ مِنْ قَبْلِ كلِّ مَنْ فِي السَّمَوَاتِ وَالأَرْضِ فِي حِيْنِ ظُهُوْرِ عَظَمَتِكَ وَ سَلْطَنَتِكَ وَطُلُوْعِ عِزِّ حُكُوْمَتِكَ بِكَلِمَة "بَلَى" كَ وَبِهَذِهِ الأَسْمَاءِ الحُسْنَى الأَعْظَمِ وَبِهَذِهِ ٱلْصِّفاتِ ٱلْعُلْيا الْأَكْرَمِ وَبِذِكْرِكَ العَلِيِّ الأَعْلَى وَبِجَمَالِكَ الأَلْطَفِ الأَصْفَى وَبِنُوْرِكَ الخَفيِّ فِي سُرَادِقِ الأَخْفَى وَبِإِسْمِكَ المُتَقَمَّصِ بِقَمِيْصِ البَلَاءِ فِي كُلِّ صَبَاحٍ وَمَسَاءٍ أَنْ تَحْفَظَ حَامِلَ هَذِهِ الوَرَقَةِ المُبَارَكةِ ثُمَّ الَّذِي يَقْرَؤُوهَا ثُمَّ الَّذِي يُلْقَى عَلَيْهَا ثُمَّ الَّذِي يَمُرُّ فِي حَوْلِ بَيْتِ الَّتِي هِيَ فِيْهَا ثُمَّ اشْفِ بِهَا كُلَّ مَرِيْضٍ وَعَلِيْلٍ وَفَقِيْرٍ عَنْ كُلِّ بَلَاءٍ وَمَكْرُوْهٍ وَآفَةٍ وَحُزْنٍ ثُمَّ اهْدِ بِهَا كُلَّ مَنْ يُرِيْدُ أَنْ يَدْخُلَ في سُبُلِ هِدَايَتِكَ وَمَنَاهِجِ فَضْلِكَ وَغُفْرَانِكَ وَإِنَّكَ أَنْتَ ٱلْعَزِيْزُ الكَافِي الشَّافِي الحَافِظُ المُعْطِي الرَّؤُوفُ الكَرِيْمُ الرَّحِيْمُ
  \end{arab}
\end{hafez}

% \newpage

% \theendnotes

\end{document}
